---
title: "Data Visualization in R"
authors: ["Orlando Joaqui Barandica"] 
date: 2021-09-27T21:13:14-05:00
categories: ["R","Xaringan","ggplot2","plotly","highcharter","dplyr" ]
tags: ["DataViz", "R","Tidyverse"]
subtitle: "Knowing how to do data science is also knowing how to communicate. Effective communication is the cornerstone of impactful data science. Either teaching data-related skills or reporting the latest results obtained in our statistical processes."
summary: "Knowing how to do data science is also knowing how to communicate. Effective communication is the cornerstone of impactful data science. Either teaching data-related skills or reporting the latest results obtained in our statistical processes."
draft: false
featured: false
image:
  caption: 'DataViz in R'
  focal_point: ""
  placement: 2
  preview_only: false
projects: []
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```


These slides will cover a mix of styles for # ️⃣DataViz. We will learn the necessary structure of the data for the adequate visualization of the information. We will work with packages like ggplot2, plotly, highchart, among others.

I present the next structure:

* Introduction
* Data preparation
* Static #️⃣DataViz
* Interactive #️⃣DataViz


## 1. Introduction

```{r embed-xaringan1, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://juniorjb5.github.io/DataViz/1_Intro/1_Intro.html#1", ratio = "16:9")
```


* Visit slides: 🔗 [Here! Introduction](https://juniorjb5.github.io/DataViz/1_Intro/1_Intro.html#1)
    - Recommendation to see in full screen (F11 - Google Chrome)



## 2. Structure and Manipulation of Data

```{r embed-xaringan2, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://juniorjb5.github.io/DataViz/2_Data/2_Data.html#1", ratio = "16:9")
```


* Visit slides: 🔗 [Here! Data Preparation & Tables](https://juniorjb5.github.io/DataViz/2_Data/2_Data.html#1)
    - Recommendation to see in full screen (F11 - Google Chrome)



## 3. Static #️⃣DataViz

```{r embed-xaringan3, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://juniorjb5.github.io/DataViz/3_ggplot2/3_ggplot2.html#1", ratio = "16:9")
```


* Visit slides: 🔗 [Here! DataViz ggplot2](https://juniorjb5.github.io/DataViz/3_ggplot2/3_ggplot2.html#1)
    - Recommendation to see in full screen (F11 - Google Chrome)
    

## 4. Interactive #️⃣DataViz

```{r embed-xaringan4, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://juniorjb5.github.io/DataViz/4_InteractiveR/4_Interactive.html", ratio = "16:9")
```



* Visit slides: [🔗 Here! Interactive graphs](https://juniorjb5.github.io/DataViz/4_InteractiveR/4_Interactive.html#1)
    - Recommendation to see in full screen (F11 - Google Chrome)




## Coming soon more content!!



